Data Processing (Julia)

### 2025-05-01 notebooks/30_data.qmd
update

```{julia}
using Discontinuity
using Dates
period = Second(60)

@@

ds.r = r[Ti(Near(ds.time))]
```

@@

```{julia}
using SPEDAS

@kwdef struct JunoEvent{D} <: AbstractEvent
    data::D
    start
    stop
    metadata = Dict()
end

@@

df.time[isnan.(df.grad)]
function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
    tmin, tmax = t_us_ds(event)
    f = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
    tlines!(f, [tmin, tmax])
    f
end
tplot(Product(b, tview), "2011-08-28T06:42:00", "2011-08-28T06:43:00")
```

>>>>

```{julia}
using Discontinuity
using Dates
using DataFrames
period = Second(60)

@@

ds.r = r[Ti(Near(ds.time))]

df = dropmissing(ds)
```

@@

```{julia}
using SPEDAS
using Discontinuity: mva_transform, tanh_model

@@

B_product = Product(b, tview)

struct FitProduct{F,P} <: Function
    f::F
    param::P
    t_fit::DateTime
end

function (p::FitProduct)(t0, t1)
    tspan = DateTime(t0):Millisecond(10):DateTime(t1)
    xspan = (tspan .- p.t_fit) / Millisecond(1)
    data = p.f.(xspan, Ref(p.param))
    return DimVector(data, Ti(tspan))
end

FitProduct(row) = FitProduct(tanh_model, row.fit_param, row.t_us_ds[1])
FitProduct(df::DataFrame, i) = FitProduct(df[i, :])

struct MVAProduct <: Function
    V
    B
    B_tspan
end

(p::MVAProduct)(t0, t1) = mva(p.V(t0, t1), p.B(p.B_tspan...))

function plot_candidate(df::DataFrame, i, toffset=Second(0); kwargs...)
    row = df[i, :]
    B_mva = MVAProduct(B_product, B_product, row.t_us_ds)
    Bl_fit_product = FitProduct(row)

    tmin, tmax = row.tstart, row.tstop
    f = tplot([B_product, B_mva, Bl_fit_product], tmin - toffset, tmax + toffset; kwargs...)
    tlines!(f, collect(row.t_us_ds))
    f
end
```

```{julia}
# 740, 1508, 4004, 4805
for i in [740, 1508, 4805]
    display(plot_candidate(df, i))
end
```
